### 2004-09-22 Documentation/part3.tex
*** empty log message ***
PH -- Added pdf support. make pdf produces a file Manual.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PART III: Reference manual
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Reference manual}

Here comes a list of all functions and their function in alphabetical order.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PART III: Module Support
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{\GLOBES\ modules}
\label{part:3}
~\\
=================================\\
This is a very raw version of the modules part, it is not clear
wether it will be an own part or just a chapter somewhere else.
In any case it should serve a reference in using modules in
Version 2.1\\
=================================\\

The ability of \GLOBES\ to use dynamically loadable modules makes it easy
to extend the functionality of \GLOBES\ at run-time and to adapt it to
new tasks in a transparent way. This part of the manual describes how 
modules are used, how they are written and compiled. Also some details
on static linking of modules will be discussed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Using modules}
\label{chap:using_modules}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Writting own modules}
\label{chap:own_modules}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Compiling modules}
\label{chap:comp_modules}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Static linking}
\label{sec:static_modules}
